Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-04 prop_letter.tex
prop_letter.tex \section{Gleason} Discussing norm...

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{assumption}{Assumption}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{example*}{Example}
\newtheorem{condition}[assumption]{Condition}

@@

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with a Born QIVPM~$\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
Moreover, with respect to a notion of distance between two states~$\rho$
and $\rho'$, $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower.

@@

\yutsung{Compare the norm we used with other distances. For example,
the trace distance defined in Sec.~9.2.1 in Nielsen and Chuang~\citep{544199}.}

@@

>>>>

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{lemma}{Lemma}[thm]
\newtheorem{cor}{Corollary}[thm]
\newtheorem{assumption}{Assumption}
\newtheorem{fact}{Fact}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem*{example*}{Example}
\newtheorem{condition}[assumption]{Condition}

@@

In contrast with the QIVPM defined in Table~\ref{tab:non-Born-QIVPM},
there is always a state consistent with a Born QIVPM $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
because $\rho\in\coreBorn\left(\left[\mu_{\rho}^{\mathrm{B}}\right]_{n},\events\right)$.
Moreover, with respect to a notion of distance between two states~$\rho$
and $\rho'$~\citep{544199}, 
\begin{equation}
\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|\,,\label{eq:norm}
\end{equation}
the collection of states consistent with $\left[\mu_{\rho}^{\mathrm{B}}\right]_{n}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower.

@@

@@

\yutsung{Following are the discussion and personal notes about our
norm and other notation of norm and distance.}

Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
in Appendix~6

Although Nielsen and Chuang~\citep{544199} in Appendix 6 follow
Simon {[}2{]} to prove theorems, it seems Simon didn't define the
norm in his book {[}2{]}, and the definition used in Nielsen and Chuang
{[}1{]} is clearly not what Simon would like to use... Figuring out
what we should use...

\begin{fact}Let $\sigma\left(\rho-\rho'\right)$ denote the set of
eigenvalues of $\rho-\rho'$. Since $\rho$ and $\rho'$ are states,
they are Hermitian~\citep{544199}, and so does $\rho-\rho'$. In
this situation, $\left\Vert \rho-\rho'\right\Vert =\max\set{\left|\lambda\right|}{\lambda\in\sigma\left(\rho-\rho'\right)}$~\citep{544199}.\end{fact}

\yutsung{End of discussion.}
